Verifying Demonstrations

### 2018-08-13 paper/conclusions.tex
edits and comments according to annotations from June 6!

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. 
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.

Of separate interest, we have also build distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they would provide individual verifiability, they would likely violate the privacy requirements.

Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on theparticipants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

>>>>

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }

Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.

Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

### 2018-08-13 paper/protocol.tex
edits and comments according to annotations from June 6!

\NewScheme{\PRIVOscheme}{PRIVO}

@@

Several entities are involved in our protocol.
First, the \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
The \ac{CA} is only involved in the setup phase.
Second, a protester is an individual who wants to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
\end{enumerate}
In general, there is one organizer and every protester will act alternatively as both participant and witness.

@@

\NewAlgorithm{\PRIVOsetup}{Setup}
\NewVariable{\sk}{sk}
\NewVariable{\spk}{spk}
\NewVariable{\ssk}{ssk}

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
During setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\NewAlgorithm{\PRIVOreg}{Reg}

@@

\subsection{Creation, join and participation to a protest and submission of proofs}%
\label{ProtocolDuring}

@@

\NewAlgorithm{\PRIVOjoin}{Join}
\NewVariable{\mfst}{manifesto}
\NewVariable{\cid}{cid}
\NewVariable{\pid}{pid}

@@

\NewVariable{\wid}{wid}

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key \(\sk_W\) and \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

@@

\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Remark that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.

\NewAlgorithm{\PRIVOparticipate}{Prticip}
\NewAlgorithm{\PRIVOwitness}{Witness}

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the participant and the witness constructs the proof share of the participant (\cref{fig:ProofFig}).
The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the participant computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the participant.
As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).

\NewAlgorithm{\PRIVOsubmit}{Submit}

>>>>

@@

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
The \ac{CA} is only involved in the setup phase.
Second, a protester is an individual who wants to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
\end{enumerate}
In general, there is one organizer and every protester will act alternatively as both participant and witness.

@@

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

@@

\subsection{Creation, join and participation in a protest and submission of proofs}%
\label{ProtocolDuring}

@@

@@

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and \sonja{the other's?}\(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

@@

\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the participant and the witness construct the proof share of the participant (\cref{fig:ProofFig}).
The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the participant computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the participant.
As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).
